---
title: "A Minimal Book Example"
author: "lennydeces"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
output:
  bookdown::gitbook: default
---

# About

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports; for example, a math equation $a^2 + b^2 = c^2$.

## Usage 

Each **bookdown** chapter is an .Rmd file, and each .Rmd file can contain one (and only one) chapter. A chapter *must* start with a first-level heading: `# A good chapter`, and can contain one (and only one) first-level heading.

Use second-level and higher headings within chapters like: `## A short section` or `### An even shorter section`.

The `index.Rmd` file is required, and is also your first book chapter. It will be the homepage when you render the book.

## Render book

You can render the HTML version of this example book without changing anything:

1. Find the **Build** pane in the RStudio IDE, and

1. Click on **Build Book**, then select your output format, or select "All formats" if you'd like to use multiple formats from the same book source files.

Or build the book from the R console:

```{r, eval=FALSE}
bookdown::render_book()
```

To render this example to PDF as a `bookdown::pdf_book`, you'll need to install XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

## Preview book

As you work, you may start a local server to live preview this HTML book. This preview will update as you edit the book when you save individual .Rmd files. You can start the server in a work session by using the RStudio add-in "Preview book", or from the R console:

```{r eval=FALSE}
bookdown::serve_book()
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

# Note {#helloworld}

<style>
  .iframe-container {
    display: flex;
    flex-wrap: wrap; /* Allow items to wrap to the next line */
    justify-content: space-between;
  }

  .iframe-container iframe {
    width: 385px; /* Adjust the width as needed */
    height: 500px; /* Adjust the height as needed */
    margin-right: 10px; /* Add spacing by adjusting this value */
  }

  .iframe-container .full-width {
    width: 780px; /* Make this iframe spread the full width */
    height: 500px; /* Adjust the height as needed */
  }
</style>

<div class="iframe-container">
  <iframe src="https://www.randymajors.org/zipcodegmap"></iframe>
  <iframe src="https://developers.google.com/public-data/docs/canonical/states_csv"></iframe>
</div>

<div class="iframe-container">
  <iframe class="full-width" src="https://www.latlong.net/"></iframe>
</div>

**Windows**

System➡️Display➡️Multiple displays➡️Detect other display➡️Detect→Buttons

Right Click on File➡️Show more options

Folder➡️Alt + Enter➡️Properties

Folder➡️Ctrl + Shift + C➡️Copy as path

Windows + P➡️Extend

Windows + X➡️U➡️U

Windows + Z

Windows + Up Arrow | Right Arrow | Down Arrow | Left Arrow

**Adobe Acrobat**

View➡️Page Display➡️Two Page Scrolling

**Word**

Review➡️Tracking➡️All Markup➡️Drop Down➡️Simple Markup | All Markup | No Markup

<!-- Note -->

---

# Resource {#welcome}

**Application**

[OPT and STEM OPT](https://www.uscis.gov/working-in-the-united-states/students-and-exchange-visitors/optional-practical-training-opt-for-f-1-students)

[Timeline](https://opttimeline.com/IOE?CASE_TY=EAD)

[I-765 Application for Employment Authorization](https://www.uscis.gov/i-765)

[I-94](https://i94.cbp.dhs.gov/I94/#/recent-search)

[ICE Form I-983](https://www.ice.gov/doclib/sevis/pdf/i983.pdf)

[E-Verify](https://www.e-verify.gov/about-e-verify/e-verify-data/how-to-find-participating-employers)

[SEVP Portal | Student and Exchange Visitor Program Portal](https://sevp.ice.gov/opt/#/login)
<br>
<br>

**Ohio**

[Findyourohio](https://www.findyourohio.com/)

[StreetLight](https://insight.streetlightdata.com/login/?/sso_auth=skilljar?next=%2F)

[TechCred](https://techcred.ohio.gov/)

[Transportation Data Management System](https://morpc.public.ms2soft.com/tcds/tsearch.asp?loc=Morpc&mod=)

[Urban Area Boundary Review Viewer](https://gis3.dot.state.oh.us/uab-review-readonly/)
<br>
<br>

**Management**

[Drawio](https://app.diagrams.net/)

[ProcessOn](https://www.processon.io/)

[Siyuan](https://b3log.org/siyuan/en/)

[Timely](https://timelyapp.com/)

[Whimsical](https://whimsical.com/ai)

[Xmind](https://xmind.app/share/)
<br>
<br>

**Survey**

[Mentimeter](https://www.mentimeter.com/app/home)

[Slido](https://www.slido.com/?experience_id=240223-z)

[SurveyMonkey](https://auth-us.surveymonkey.com/login?state=hKFo2SB0eVdrbDlmUHVCanA4NW9xTjJ0eHpfQ1p6c3VyVXBGdaFupWxvZ2luo3RpZNkgUEltZ2JWUUdwdUkwMklsTU92aXpHZUFTOTYxZkxQU0ejY2lk2SBzQTM0RFVtUUE0RUlySkM3cTlRdVBDZjFUNzc4QmZMdg&client=sA34DUmQA4EIrJC7q9QuPCf1T778BfLv&protocol=oauth2&prompt=login&scope=openid%20profile%20email&redirect_uri=https%3A%2F%2Fwww.surveymonkey.com%2Flogin%2Fcallback&ut_ctatext=Log%20in&ut_source=sem_lp&ut_source2=sem&ut_source3=desktop-header-cta&sm.amp_did=298190b2-87d3-4312-9507-d990ba110712&sm.amp_sid=1711919419251&sm.locale=en&sm.country=US&sm.subdomain=www&response_type=code&response_mode=query&nonce=RFJPUWRqRldzS2NpcjBwaUh5R3ViSVRha0ZTRlNodjE2TWs3dGxyUThoSg%3D%3D&code_challenge=t5Pncc9fis59tpIh0qSelfUXG2VOsZKZJXyz2dROPc8&code_challenge_method=S256&auth0Client=eyJuYW1lIjoiYXV0aDAtc3BhLWpzIiwidmVyc2lvbiI6IjIuMC4xIn0%3D#/login)
<br>
<br>

**Paper**

[Connected Papers](https://www.connectedpapers.com/)

[EndNote](https://endnote.com/)

[Google Scholar](https://scholar.google.com/)

[Library Genesis](https://libgen.li/)

[MyBib](https://www.mybib.com/#/projects/Dp1Abo/citations)

[ResearchGate](https://www.researchgate.net/)

[ResearchRabbit](https://www.researchrabbit.ai/)

[Scidown](https://www.scidown.cn/)

[Sci-Hub](https://sci-hub.41610.org/)

[Web of Science](https://www.webofscience.com/wos/author/search)
<br>
<br>

**Writing**

[Copy.ai](https://www.copy.ai/)

[DeepL](https://www.deepl.com/en/translator)

[DocHero](https://www.dochero.ai/en)

[Grammarly](https://www.grammarly.com/plagiarism-checker)

[MagicPen](https://magickpen.com/)

[Paper Digest](https://www.paperdigest.org/review/)

[QuillBot](https://quillbot.com/)

[Writefull](https://www.writefull.com/)

[Writesonic](https://writesonic.com/)

[Zotero](https://www.zotero.org/)
<br>
<br>

**Design**

[Canva](https://www.canva.com/templates/)

[Diagram](https://diagram.com/)

[Figma](https://www.figma.com/)

[Galileo AI](https://www.usegalileo.ai/explore)

[Logoai](https://www.logoai.com/logo-maker)

[Looka](https://looka.com/)

[Noya](https://www.noya.io/ui)

[Uizard](https://uizard.io/templates/)
<br>
<br>

**Drawing**

[Adobe Firefly](https://www.adobe.com/products/firefly.html?gclid=Cj0KCQjwk6SwBhDPARIsAJ59Gwd5ryWm7_kkdRXLvJCASelBPtk88u8PidKCH0UEBeuP_89Y1cbLY6gaAnLmEALw_wcB&sdid=JM4FW6VL&mv=search&mv2=paidsearch&ef_id=Cj0KCQjwk6SwBhDPARIsAJ59Gwd5ryWm7_kkdRXLvJCASelBPtk88u8PidKCH0UEBeuP_89Y1cbLY6gaAnLmEALw_wcB:G:s&s_kwcid=AL!3085!3!677394754238!e!!g!!adobe%20firefly!19870733758!148140507838&gad_source=1)

[Booltool](https://booltool.boolv.tech/home)

[Clipdrop](https://clipdrop.co/)

[Dreamlike.art](https://dreamlike.art/)

[DreamUp](https://www.dreamup.com/)

[Flaticon](https://www.flaticon.com/)

[Hotpot.ai](https://hotpot.ai/)

[Hugging Face](https://huggingface.co/spaces/stabilityai/stable-diffusion)

[Jasper](https://www.jasper.ai/)

[Lexica](https://lexica.art/)

[Midjourney](https://www.midjourney.com/home)
<br>
<br>

**Music**

[Audo Studio](https://audo.ai/)

[AssemblyAI](https://www.assemblyai.com/)

[FakeYou](https://fakeyou.com/)

[LALAL.AI](http://LALAL.AIhttps://www.lalal.ai/?gad_source=1&gclid=Cj0KCQjwk6SwBhDPARIsAJ59Gwe8R6D_cisJF45mTx4pgQz01WhtUM2gqvDKZGUDPRqT4sIvC4rC2y4aAiX3EALw_wcB)

[NaturalReader](https://www.naturalreaders.com/)

[Resemble.AI](https://www.resemble.ai/)
<br>
<br>

**Video**

[DreamFace](https://dreamfaceapp.com/)

[DeepBrain](https://www.deepbrain.io/)

[HeyGen](https://www.heygen.com/)

[Lumen5](https://lumen5.com/)

[Rephrase.ai](https://www.rephrase.ai/)

[Runway](https://runwayml.com/)

[Synthesia](https://www.synthesia.io/)

[Synthesys](https://synthesys.io/)
<br>
<br>

**Plot**

[Hiplot](https://hiplot.com.cn/home/index.en.html)

[ImageGP](https://www.bic.ac.cn/ImageGP/)
<br>
<br>

**Presentation**

[Decktopus AI](https://www.decktopus.com/?gad_source=1&gclid=Cj0KCQjwk6SwBhDPARIsAJ59Gwc4xWCC-ZY81-gYiYl_NSnhkTYhHrSkNBFMRRkgU9aTMm5EjFl7ZigaAnutEALw_wcB)

[Powerpresent AI](https://powerpresent.ai/)
<br>
<br>

**Coding**

[Code Translator](https://ai-code-translator.vercel.app/)

[CodiumAI](https://codeium.com/)
<br>
<br>

**Productivity**

[AI Chat](https://deepai.org/chat)

[Anthropic](https://claude.ai/login?returnTo=%2F)

[ChatBA](https://www.chatba.com/)

[ChatGPT](https://chat.openai.com/)

[Perplexity](https://www.perplexity.ai/)

[Poe](https://poe.com/login)
<br>
<br>

**Plagiarism**

[Turnitin](https://www.turnitin.com/)

[Cite This For Me](https://www.citethisforme.com/)

<!-- Resource -->

---

# Life

ATAS and UGC is there to help you navigate your academic path.

You also have ASTC to support you on your academic path. CAPS will always be there to listen and to help.

We have CPO to promote a safe SBU community.

USG and ISO is there to bring campus involvement and student activity to your college life.

Career Center has the resources and the"HandShake" to prepare you to the future work environment.

<details>
  <summary>***Game***</summary>
  Daifugo
  
  Killers of the Three Kingdoms
  
  Mahjong
  
  Murder Mystery
  
  Relay
  
  Werewolf
  
  Who is undercover
  
  You Draw, I Guess
</details>

<br>

1. Scan Your Documents

use the scanners provided or your smartphone to take a photo of each of your immigration documents:
  - Passport
  
  - Visa
  
  - Form I-20 / DS-2019
  
  - Admission Stamp
  
  - Previous I-20s (Transfer Students)
  
  <br>

2. Retrieve your I-94
  - Visit [https://i94.cbp.dhs.gov](https://i94.cbp.dhs.gov)
  
  - Check `'yes'` to consent to DHS' terms, click submit
  
  - Enter all required passport information
  
  - Click `“Get Most Recent I-94”`
  
  - Save as a `PDF file` on the desktop
  
  <br>
  
3. Pick up some life skills
  - Cooking Skill
    - Meat
      - Bacon
      - Beaf
      - Chicken
      - Pork
      - Shrimp
    - Vegetable
      - Bamboo Shoots
      - Bean Curd
      - Bok Choy
      - Cabbage
      - Carrot
      - Celery
      - Cucumber
      - Enoki
      - Green Pepper
      - Ham
      - Lettuce
      - Mushroom
      - Potato
      - Turnip
    - Other
      - Egg
      - Tofu
      - Tomato
      - Woodear
  - Driving Skill
    - Local
    - Collector
    - Arterial
    - Interstate
  - Academic Skill
    - Passive Learning
    - Active Learning
  - Professional Skill
    - Time Management
    - Leadership
    - Speech
    - Confidence
    - Collaboration
    - Communication
    - Conflict Resolution
    - Critical Thinking
    - Creativity
    - Attention to Details
    - Problem Solving
    - Decision Making
    
<!-- Skill -->

---

# Software and Platform

## Software
Google Chrome

Word

PowerPoint

Excel

JMP

Numbers

Tableau

Tableau Prep Builder

VOSviewer

GeoDa

QGIS

R Studio

Visual Studio Code

Adobe InDesign

Adobe Illustrator

Adobe Photoshop

Zoom

## Platform

Simplilearn

Ryan Farish

V.K

Pianoboy

Charming Data

3Blue1Brown

SketchUp

One Skill PowerPoint

Open Geospatial Solutions

SourceCAD

Tutorialspoint

Geography King

Learnit Training

Wendover Productions

Cindy Stats

Art of Visualization

Webflow

Academic Lesson

Big Data TX

Photoshop Tutorials by Layer Life

MIT OpenCourseWare

Engineering Academy

Kim Hyung Suk - Topic

CE 355 Principles of Transportation Engineering

Vizual Intelligence

Ruth M Hummel

Julian Parris

Analytics University

BurkeyAcademy

The Real Estate Classroom

US Realty Training

USLawEssentials

CitiesX

Serrano.Academy

StataCorp LLC

Quimbee

PrepAgent

Skills Factory

FordhamStats

Jalayer Academy

The Teacher

Programming with Mosh

Sele Training

Envato Tuts+

City Beautiful

Visme

Map & GIS Library

Mr. Beat

Planetizen Courses

GeoGebra

The Organic Chemistry Tutor

Aaron Shkoler

Marginal Revolution University

Les Enfants du Top 50

Simplify Insights

The Information Lab

freeCodeCamp.org

Tableau

CS50

JMP Statistical Discovery

MyOnlineTrainingHub

ritvikmath

StatQuest with Josh Starmer

GeoDa Software

Logan Burchett

aquarius20011989

zedstatistics

# Philosophy

<h3>A</h3>
Add, Create, Insert

Analyze

Annotate, Mark

Automatic Fill

<h3>B</h3>
Beta

Bookmark, Favorite

<h3>C</h3>
Calculate, Derive

Certificate, Progress

Cloud

Code

Compare

Customize

<h3>E</h3>
Edit

Explore

<h3>F</h3>
File

Filter

Format/Style

<h3>H</h3>
Help

Hide

History

<h3>L</h3>
Layer

Layout

<h3>M</h3>
Manage, Organize, Reorder

Mode

<h3>N</h3>
Note

<h3>O</h3>
Open

<h3>P</h3>
Parameter

Profile

<h3>R</h3>
Reorder

Recommendation

Reset

Review

<h3>S</h3>
Save, Version

Search

Select

Setting

Share

Sort

<h3>T</h3>
Tag

Template

Test

Time

Tool

Translation

Tutorial

<h3>V</h3>
Version

View

<h3>W</h3>
Weather

Window

<h3>Other</h3>

Apply + Okay

Back + Forward

<!-- Philosophy -->
